The first high-redshift changing-look quasars

### 2019-12-10 tex/CIV_CLQs_20191210.tex
submitting tomorrow...

\title[High-redshift CLQs]{The first high-redshift Changing Look Quasars}

\author[Ross {\it et al.}]
{Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
Matthew Graham$^{2}$,
Giorgio Calderone$^{3}$, 
K. E. Saavik Ford$^{4,5,6}$,  
\newauthor Barry McKernan$^{4,5,6}$  and Daniel Stern$^{7}$  
\\
%%  List of institutions
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
$^{4}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{5}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{6}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{7}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first ``Changing-Look'' quasars at
high redshift.  This is also the first time the changing-look
behaviour has been seen in a high-ionization emission line.  SDSS
J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
their observed optical light curves, and subsequent spectroscopy shows
significant changes in the \civ\ broad emission line, with both line
collapse and emergence being displayed in rest-frame timescales of
$\sim$240-1640 days.  These are very quick changes, especially when
considering virial black hole mass estimates have all three quasars
with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
measurements from the three quasars show changes in the
continuum-equivalent width plane with the CLQs seen to be on the edge
of the full population distribution, and showing indications of an
intrinsic Baldwin Effect. We put these observations in context with
recent ``state-change'' models, but note that even in their
`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
luminosity.
\end{abstract}

@@

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs)
have now been assembled \citep[e.g.][]{MacLeod2019, Graham2019b}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, CLQs can potentially be thought of as
the extension to the BELs of quasar continuum variability \citep[e.g.,
][]{MacLeod2012} whereas the CSQs have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
this paper, we use the term `Changing Look', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.

\begin{table*}
  \begin{centering}
    \begin{tabular}{l r  r r   lll lll  r r}
      \hline  \hline 
      Line                 & $\lambda$ &  Transition  & Ionization   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
                              &  / \AA\    & energy / eV &  energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & ($\times10^{8}$  / s$^{-1}$)               \\      \hline
      H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
      H Ly$\alpha$  &  1215.670  & 10.1988    & 13.5984       & 1$s$                     & $^2$S      & 1/2          & 2                             &                                 &             &  82 259.2       &  4.67  \\
      \nv                  &  1238.821  & 10.0082    &  97.8901      &  1$s^{2}$2$s$      &  $^{2}$S   &  1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40   \\
      \nv                  &  1242.804  &  9.9762     &  97.8901      &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2        &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37 \\
      \civ                 &  1548.187  &  8.0083     &  64.4935      &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65  \\
      \civ                 &  1550.772  &  7.9950     &  64.4935      & 1$s^{2}$2$s$        &  $^{2}$S   & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64  \\
      \heii               &   1640.474  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35 \\
      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 957.4       & 1.73 \\
      \ciii                 &  1906.683  &  6.5026     & 47.8878       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ \\
      \ciii                 &  1908.734  &  6.4956     & 47.8878       & 1$s^{2}$2$s^{2}$   &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{-6}$  \\
       \mgii              &  2795.528  &  4.4338     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60  \\
      \mgii               &  2802.705  &  4.4224     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 \\
      H Ba $\beta$   &  4861.333  &  2.5497     & 13.5984       & 2                              &                 &               & 4                             &                                 &              &  20 564.8       & 0.0842  \\
      \hline   
      \hline
    \end{tabular}
    \caption{
      Strong UV/optical spectral emission lines in quasars, and their
      atomic data.  Data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.  The Transition Energies are
      $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
      energy required to ionize the given species, e.g. 64.49 eV are needed
      to create a \cv\ ion.  Transitions Level configurations are given in
      standard spectroscopic notation $A_{i,j}$ are transition
      probabilities.  Data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.}
    \label{tab:atomic_lines}
  \end{centering}
\end{table*}

CLQs to date have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent work report on discoveries of \mgii Changing-look
AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
primarily been at redshifts $z<1$.

While there have been many studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL quasars; see Table 1 of][]{Hemler2019} or the Baldwin Effect
\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the Equivalent Width (EW) of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ\ and
indeed \ciii have not to this point been reported.

\begin{table*}
  \centering
  \begin{tabular}{l l   r ll  r r l}
    \hline 
    \hline 
    \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
                                         &                                        &   (mag)      &                                 &                                             &  Time (secs) &   Plate-FiberID  & \\
    \hline  
                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & \\
 J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &          \\
                                       &                                       &                     &                               &                                              &                      &                               &                               \\
                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & \\
J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & \\
                                      & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                      &                                         &                    &                                 &                                            &                      &                              &                                 \\
                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & \\
 J222818.7+220102.9   & 2.222                               &                    &  56960                     & BOSS                                    &  4500            &   7582-790          & eBOSS reobservation \\ 
                                     &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
    \hline \hline   
  \end{tabular}
  \caption{Details of our spectroscopic observations.  Redshift errors are
    typically $\pm$0.002.  SDSS, BOSS and eBOSS spectra have
    $\mathcal{R}\sim$2,000.  DBSP: Double Spectrograph on the Palomar
    200-inch telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
    I 10m telescope.} 
  \label{tab:obs_notes}
\end{table*}

Here, we present new results for three quasars which show dramatic
changes in their \civ\ and \ciii broad emission line properties as
well as in their underlying continuum. These are some of the first
examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering of lower energy photons to
higher energies.

Details of the atomic transitions that produce strong rest-frame
UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
1548.202 and 1550.774~\AA\ for the \civ\ doublet
\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
required for doubly-ionised C~III to become triply-ionised \civ.
64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
energy corresponds to a thermal temperature of $T \gtrsim$
4$\times10^{5}$, implying a heating energy source of (soft) X-ray
photons.

\citet{Wilhite2006} examine \civ\ variability in a sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the \civ\ line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The \civ\ lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$
SDSS quasars, concentrating on the properties of the \civ\ emission
line. These authors consider two well-known effects involving the
\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
with respect to the systemic redshift.  We denote the velocity offset
of emission lines as $V_{\rm off}$ and use the convention that a
positive $V_{\rm off}$ value means the line is blueshifted while a
negative $V_{\rm off}$ value means the line is redshifted.
\citet{Richards2011} find the blueshift of the \civ\ emission line, is
found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
\sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
\sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
also find the BEff is present in both the RQ and RL studied samples.
These author conclude that these two \civ\ parameters (EQW and
blueshift) are capturing an important trade-off between ``disk'' and
``wind'' components in the disk-wind model of accretion disks
\citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
one dominating over the other depending on the shape of the SED.

Using the multi-epoch spectra of 362 quasars from the Sloan Digital
Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
emission relative to \mgii emission, and its dependence on quasar
properties. These authors confirm that high-blueshift sources tend to
have low \civ\ EWs, and that the low-EW sources span a range of
blueshift. Other high-ionization lines, such as \heii, also show
similar blueshift properties. The ratio of the line width of \civ\ to
that of \mgii increases with blueshift. \citet{Sun2018} also find that
quasar variability might slightly enhance the connection between the
\civ\ blueshift and EW, though further investigation here is
warranted. There is also the finding that the objects with that
largest blueshifts are less variable and tend to have higher Eddington
ratios. \citet{Sun2018} explain their results these by suggesting that
quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
spectral index, $\alpha_{\rm ox}$) and thus become {\it
softer} with {\it increasing Eddington ratio} along with the presence
of X-ray shielding by the inner accretion disk. However, a high
Eddington ratio alone might be an insufficient condition for the \civ\
blueshift. Recent investigations also include \citet{Meyer2019} and
\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
which we will compare our results to.

%%    P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to systematically
access and report on the CLQ phenomenon at high ($z>2$)
redshift. While accessing this phenomenon at an earlier cosmic epoch
is somewhat interesting, the main value of this study is we move from
the low-ionization energy Balmer emission line series to the
high-ionization emission lines, in particular \civ\ $\lambda$1549.

@@

\subsection{Multi-Wavelength Properties}
{\bf DS to write something on FIRST non-detections; possibly check the X-rays too?} \\
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
of the {\it Wide-field Infrared Survey Explorer} ({\it WISE}) mission
\citep[2010 January; ][]{Wright2010} through the fifth-year of {\it
NEOWISE-R} operations \citep[2018 December; ][]{Mainzer2011}. The {\it
WISE}WISE scan pattern leads to coverage of the full-sky approximately
once every six months (a ``sky pass''), but the satellite was placed
in hibernation in 2011 February and then reactivated in 2013
October. Hence, our light curves have a cadence of 6 months with a
32-month sampling gap.

@@

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the narrow peak of the \civ\ line.  No
narrow components are considered for several reasons: in the epochs of
highest brightness the ``narrow'' component would have FWHM~$\sim2-3
\times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
genuine narrow lines ($\lesssim$10$^{3}$ km s$^{-1}$); by allowing a
second component, to have such large widths their parameters would
become highly degenerate with the ``broad'' components, and the latter
would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); and by
neglecting the narrow components we have a consistent fit across all
epochs.

>>>>

\title[High-redshift CLQs]{The first high-redshift changing-look quasars}

\author[Ross {\it et al.}]
{Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
Matthew J. Graham$^{2}$,
Giorgio Calderone$^{3}$, 
K. E. Saavik Ford$^{4,5,6}$,  
\newauthor Barry McKernan$^{4,5,6}$  and Daniel Stern$^{7}$  
\\
%%  List of institutions
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
$^{4}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{5}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{6}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{7}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first sample of changing-look quasars (CLQs) at
high redshift.  This is also the first time the changing-look
behaviour has been seen in a high-ionisation emission line.  SDSS
J1205+3422, J1638+2827, and J2228+2201 show interesting behaviour in
their observed optical light curves, and subsequent spectroscopy shows
significant changes in the \civ\ broad emission line, with both line
collapse and emergence being displayed in rest-frame timescales of
$\sim$240-1640 days.  These are rapid changes, especially when
considering virial black hole mass estimates have all three quasars
with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
measurements from the three quasars show changes in the
continuum-equivalent width plane with the CLQs seen to be on the edge
of the full population distribution, and showing indications of an
intrinsic Baldwin effect. We put these observations in context with
recent state-change models, but note that even in their
low-state, the \civ\ CLQs are above $\sim$10\% in Eddington
luminosity.
\end{abstract}

@@

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963}.
Dramatic changes
in the broad emission lines (BELs) of quasars has only recently been
identified \citep[e.g., ][]{LaMassa2015}.  Samples of over 100
``changing-look'' quasars (CLQs) or ``changing-state'' quasars (CSQs)
have now been assembled \citep[e.g.,][]{MacLeod2019, Graham2019b}. The
community uses both these terms as a cover for the underlying
physics. For sake of argument, CLQs can potentially be thought of as
the extension to the BELs of quasar continuum variability \citep[e.g.,
][]{MacLeod2012} whereas the CSQs have a state-transition similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018, Ruan2019a}. In
this paper, we use the term ``changing-look'', as we are currently
agnostic, and confessedly ignorant, to the underlying physical
processes.

\begin{table*}
  \begin{centering}
    \begin{tabular}{l r  r r   lll lll  r r}
      \hline  \hline 
      Line                 & $\lambda$ &  Transition  & Ionisation   &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\

                              &  / \AA\    & Energy / eV &  Energy / eV  &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    & / $10^{8}$ s$^{-1}$               \\      \hline
      H LyLim           &   912.324   & 13.5984    & 13.5984        & 1$s$                    & $^2$S     & 1/2          & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{-6}$  \\
      H Ly$\alpha$  &  1215.670  & 10.1988    & 13.5984       & 1$s$                     & $^2$S      & 1/2          & 2                             &                                 &             &  82 259.2       &  4.67  \\
      \nv                  &  1238.821  & 10.0082    &  97.8901      &  1$s^{2}$2$s$      &  $^{2}$S   &  1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40   \\
      \nv                  &  1242.804  &  9.9762     &  97.8901      &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2        &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37 \\
      \civ                 &  1548.187  &  8.0083     &  64.4935      &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65  \\
      \civ                 &  1550.772  &  7.9950     &  64.4935      & 1$s^{2}$2$s$        &  $^{2}$S   & 1/2         & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64  \\
      \heii               &   1640.474  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  5/2        &  60 958.0       & 10.35 \\
      \heii               &   1640.490  &  7.5578     & 54.4178       & 2$p$ 	      &  $^{2}$P$^{{\rm o}}$ &  3/2  &  3$d$ 	                 & $^2$D                  &  3/2        &  60 957.4       & 1.73 \\
      \ciii                 &  1906.683  &  6.5026     & 47.8878       & 1$s^{2}$2$s^{2}$   &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-11}$ \\
      \ciii                 &  1908.734  &  6.4956     & 47.8878       & 1$s^{2}$2$s^{2}$   &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{-6}$  \\
       \mgii              &  2795.528  &  4.4338     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60  \\
      \mgii               &  2802.705  &  4.4224     & 15.0353       & 2$p^{6}$3$s$        &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 \\
      H Ba $\beta$   &  4861.333  &  2.5497     & 13.5984       & 2                              &                 &               & 4                             &                                 &              &  20 564.8       & 0.0842  \\
      \hline   
      \hline
    \end{tabular}
    \caption{
      Strong UV/optical spectral emission lines in quasars, and their
      atomic data.  Data from the NIST Atomic Spectra Database
      \citep{Kramida2018, Kramida2019}.  The transition energies are
      $E=hc/\lambda$ for the given wavelength. The ionisation energy is the
      energy required to ionise the given species, e.g., 64.49 eV is needed
      to create a \cv\ ion.  Transitions level configurations are given in
      standard spectroscopic notation, with $A_{i,j}$ denoting the transition
      probabilities.}
    \label{tab:atomic_lines}
  \end{centering}
\end{table*}

CLQs to date have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent works report on discoveries of \mgii changing-look
AGN \citep{Guo2019, Homan2019}. However, current CLQ studies have
primarily been at redshifts $z<1$.

While there have been many studies on triply ionised carbon, i.e.,
\civ, these have tended to focus on broad absorption line quasars
\citep[e.g., Table 1 of][]{Hemler2019} or the Baldwin effect
\citep{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: {\it (i)} the {\it
global} (or {\it ensemble}) Baldwin effect, which is an
anti-correlation between the equivalent width of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN, and {\it (ii)} the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ\ and
indeed \ciii have not to this point been reported.

\begin{table*}
  \centering
  \begin{tabular}{l l   r ll  r r l}
    \hline 
    \hline 
    \multirow{2}{*}{Object} & \multirow{2}{*}{Redshift} & $g$-band & \multirow{2}{*}{MJD} & \multirow{3}{*}{Instrument} & Exposure      &   SDSS               & \multirow{2}{*}{Notes} \\
                                         &                                        &   / mag      &                                 &                                             &  time / sec &   Plate-FiberID  & \\
    \hline  
                                       & 2.068                              & 18.27          &  53498                   & SDSS                                     &  8057            & 2089-427             & \\
 J120544.7+342252.4     & 2.071                             &                    &  58538                   & DBSP                                     &  1800            &  ---                      &  Average conditions \\
                                       & 2.071                             &                     &  58693                  & DBSP                                      &  2400            &  ---                      &          \\
                                       &                                       &                     &                               &                                              &                      &                               &                               \\
                                      & 2.185                              & 19.77           &  54553                   & SDSS                                     &   4801            &  2948-614              & \\
J163852.9+282707.7     & 2.186                              &                    &  55832                     & BOSS                                    &   3600            &  5201-178            & \\
                                      & 2.182                              &                     &  58583                     & LRIS                                    &  1800              &  ---                      & \\
                                      &                                         &                    &                                 &                                            &                      &                              &                                 \\
                                      & 2.217                               & 19.97          &  56189                    &  BOSS                                    &  2700            &   6118-720          & \\
 J222818.7+220102.9   & 2.222                               &                    &  56960                     & BOSS                                    &  4500            &   7582-790          & eBOSS reobservation \\ 
                                     &  2.222                               &                    &  58693                    &  DBSP                                    & 2400             &    ---                        &    \\
    \hline \hline   
  \end{tabular}
  \caption{Details of our spectroscopic observations.  Redshift errors are
    typically $\pm$0.002.  SDSS, BOSS and eBOSS spectra have
    $\mathcal{R}\sim$2,000.  DBSP: Double Spectrograph on the Palomar
    200-inch telescope.  LRIS: Low Resolution Imaging Spectrometer on Keck
    I 10m telescope.} 
  \label{tab:obs_notes}
\end{table*}

Here, we present new results for three quasars which show dramatic
changes in their \civ\ and \ciii broad emission line properties as
well as in their underlying continuum. These are some of the first
examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionisation potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering of lower energy photons to
higher energies.

Details of the atomic transitions that produce strong rest-frame
UV/optical lines in quasars are given in
Table~\ref{tab:atomic_lines}. In this paper we use the wavelengths of
1548.202 and 1550.774~\AA\ for the \civ\ doublet
\citep{Kramida2018}. For ionisation energies, 47.89 eV (3.519 Ry) is
required for doubly-ionised C~III to become triply-ionised \civ.
64.49 eV (4.74 Ry) is the energy needed to ionize \civ\ itself. This
energy corresponds to a thermal temperature of $T \gtrsim$
4$\times10^{5}$ K, implying a heating energy source of (soft) X-ray
photons.

\citet{Wilhite2006} examine \civ\ variability in a sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the \civ\ line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center or skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The \civ\ lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.

\citet{Richards2011} explored the broad emission line region in over 30,000 $z > 1.54$
SDSS quasars, concentrating on the properties of the \civ\ emission
line. These authors consider two well-known effects involving the
\civ\ emission line: {\it (i)} the anti-correlation between the \civ\
equivalent widths (EWs) and luminosity (i.e., the Baldwin Effect;
BEff) and {\it (ii)} the blueshifting of the peak of \civ\ emission
with respect to the systemic redshift.  We denote the velocity offset
of emission lines as $V_{\rm off}$ and use the convention that a
positive $V_{\rm off}$ value means the line is blueshifted while a
negative $V_{\rm off}$ value means the line is redshifted.
\citet{Richards2011} find the blueshift of the \civ\ emission line, is
found to be nearly ubiquitous, with a mean shift of $V_{\rm off}
\sim$810 km s$^{-1}$ for radio-quiet (RQ) quasars and $V_{\rm off}
\sim$360 km s$^{-1}$ for radio-loud (RL) objects. \citet{Richards2011}
also find the BEff is present in both the RQ and RL studied samples.
These author conclude that these two \civ\ parameters (EQW and
blueshift) are capturing an important trade-off between ``disk'' and
``wind'' components in the disk-wind model of accretion disks
\citep[e.g.,][]{Murray1995, Elvis2000, Proga2000, Leighly2004b}, with
one dominating over the other depending on the shape of the SED.

Using the multi-epoch spectra of 362 quasars from the Sloan Digital
Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
emission relative to \mgii emission, and its dependence on quasar
properties. These authors confirm that high-blueshift sources tend to
have low \civ\ EWs, and that the low-EW sources span a range of
blueshift. Other high-ionisation lines, such as \heii, also show
similar blueshift properties. The ratio of the line width of \civ\ to
that of \mgii increases with blueshift. \citet{Sun2018} also find that
quasar variability might slightly enhance the connection between the
\civ\ blueshift and EW, though further investigation here is
warranted. There is also the finding that the objects with that
largest blueshifts are less variable and tend to have higher Eddington
ratios. \citet{Sun2018} explain their results these by suggesting that
quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
spectral index, $\alpha_{\rm ox}$) and thus become {\it
softer} with {\it increasing Eddington ratio} along with the presence
of X-ray shielding by the inner accretion disk. However, a high
Eddington ratio alone might be an insufficient condition for the \civ\
blueshift. Recent investigations also include \citet{Meyer2019} and
\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
which we will compare our results to.

%%    P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to systematically
access and report on the CLQ phenomenon at high ($z>2$)
redshift. While accessing this phenomenon at an earlier cosmic epoch
is somewhat interesting, the main value of this study is we move from
the low-ionisation energy Balmer emission line series to the
high-ionisation emission lines, in particular \civ\ $\lambda$1549.

@@

\subsubsection{Multi-Wavelength Properties}
{\bf DS to write something on FIRST non-detections; possibly check the X-rays too?} \\
Mid-infrared data (3.4 and 4.6$\mu$m) is available from the beginning
of the {\it Wide-field Infrared Survey Explorer} ({\it WISE}) mission
\citep[2010 January; ][]{Wright2010} through the fifth-year of {\it
NEOWISE-R} operations \citep[2018 December; ][]{Mainzer2011}. The {\it
WISE}WISE scan pattern leads to coverage of the full-sky approximately
once every six months (a ``sky pass''), but the satellite was placed
in hibernation in 2011 February and then reactivated in 2013
October. Hence, our light curves have a cadence of 6 months with a
32-month sampling gap.

@@

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the narrow peak of the \civ\ line.  No
narrow components are considered for several reasons: in the epochs of
highest brightness the ``narrow'' component would have FWHM~$\sim2-3
\times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
genuine narrow lines ($\lesssim$10$^{3}$ km s$^{-1}$); by allowing a
second component, to have such large widths their parameters would
become highly degenerate with the ``broad'' components, and the latter
would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); moreover, by
neglecting the narrow components, we have a consistent model across all
epochs.
